Import_Map

### 2024-06-06 Code/Plots_ProNicheMap.Rmd
put axis labels back on

```{r read spectral depth backdrop}
DepthBackdrop <- readPNG("DepthBackdrop.png")
# Get dimensions of the image
width <- dim(DepthBackdrop)[2]
height <- dim(DepthBackdrop)[1]

@@

```{r, Niches figures, fig.height = 10, fig.width = 8, warning = FALSE}
NichesFullO2North <- PhotoperiodDepthFullO2 %>%
  filter(lat == 45) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 5) %>% 
mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
         lat = factor(lat, levels = c("45", "0"))) %>%
ggplot()+
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
            size = 0.5, alpha = 0, show.legend = TRUE)+
  labs(title = "Full Oxygen") +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
    facet_grid(rows = vars(lat),
              cols = vars(DayofYear),
              labeller = labeller(lat = label_both, DayofYear = label_both)) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
   # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 3
  )  +
  guides(color = "none") +
  theme_bw()+
 theme(strip.text = element_text(size = 10),
        axis.title = element_blank(),
        # strip.text.x = element_text(size = 20),
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x.bottom = element_blank(),
        axis.ticks.y.left = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        plot.margin = unit(c(0,30,0,0), "pt"))

@@

NichesFullO2Equat <- PhotoperiodDepthFullO2 %>%
  filter(lat == 0) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 5) %>% 
mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
         lat = factor(lat, levels = c("45", "0"))) %>%
ggplot()+
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
            size = 0.5, alpha = 0, show.legend = TRUE)+
  # labs(title = "Full Oxygen") +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
    facet_grid(rows = vars(lat),
              cols = vars(DayofYear),
              labeller = labeller(lat = label_both)) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
   # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 3
  )  +
  guides(color = "none") +
  theme_bw() +
 theme(strip.text.x = element_blank(),
       strip.text.y = element_text(size = 10),
        axis.title = element_blank(),
        # strip.text.x = element_text(size = 20),
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x.bottom = element_blank(),
        axis.ticks.y.left = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank())

@@

NichesOMZNorth <- PhotoperiodDepthOMZ %>%
  filter(lat == 45) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 5) %>% 
mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
         lat = factor(lat, levels = c("45", "0"))) %>%
ggplot()+
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
            size = 0.5, alpha = 0, show.legend = TRUE)+
   labs(title = "OMZ") +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
    facet_grid(rows = vars(lat),
              cols = vars(DayofYear),
              labeller = labeller(lat = label_both)) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
   # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 3
  )  +
  guides(color = "none") +
  theme_bw() +
 theme(strip.text.x = element_blank(),
       strip.text.y = element_text(size = 10),
        axis.title = element_blank(),
        # strip.text.x = element_text(size = 20),
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x.bottom = element_blank(),
        axis.ticks.y.left = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank())

@@

NichesOMZEquat <- PhotoperiodDepthOMZ %>%
  filter(lat == 0) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 5) %>% 
mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
         lat = factor(lat, levels = c("45", "0"))) %>%
ggplot()+
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
            size = 0.5, alpha = 0, show.legend = TRUE)+
  # labs(title = "Full Oxygen") +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
    facet_grid(rows = vars(lat),
              cols = vars(DayofYear),
              labeller = labeller(lat = label_both)) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
   # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 3
  )  +
  guides(color = "none") +
  theme_bw() +
 theme(strip.text.x = element_blank(),
       strip.text.y = element_text(size = 10),
        axis.title = element_blank(),
        # strip.text.x = element_text(size = 20),
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x.bottom = element_blank(),
        axis.ticks.y.left = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank())

@@

```{r}

>>>>

```{r read spectral depth backdrop}

library("png")
DepthBackdrop <- readPNG("DepthBackdrop.png")
# Get dimensions of the image
width <- dim(DepthBackdrop)[2]
height <- dim(DepthBackdrop)[1]

@@

```{r, Niches figures, fig.height = 10, fig.width = 8, warning = FALSE}
NichesFullO2North <- PhotoperiodDepthFullO2 %>%
  filter(lat == 45) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 5) %>% 
mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
         lat = factor(lat, levels = c("45", "0"))) %>%
ggplot()+
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
            size = 0.5, alpha = 0, show.legend = TRUE)+
  labs(title = "Full Oxygen") +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
    facet_grid(rows = vars(lat),
              cols = vars(DayofYear),
              labeller = labeller(lat = label_both, DayofYear = label_both)) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
   # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 3
  )  +
  guides(color = "none") +
  theme_bw()+
 theme(strip.text = element_text(size = 10),
        axis.title = element_blank(),
        # strip.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 10),
        axis.text.x = element_blank(),
        axis.ticks.x.bottom = element_blank(),
        axis.ticks.y.left = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        plot.margin = unit(c(0,30,0,0), "pt"))

@@

NichesFullO2Equat <- PhotoperiodDepthFullO2 %>%
  filter(lat == 0) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 5) %>% 
mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
         lat = factor(lat, levels = c("45", "0"))) %>%
ggplot()+
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
            size = 0.5, alpha = 0, show.legend = TRUE)+
  # labs(title = "Full Oxygen") +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
    facet_grid(rows = vars(lat),
              cols = vars(DayofYear),
              labeller = labeller(lat = label_both)) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
   # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 3
  )  +
  guides(color = "none") +
  theme_bw() +
 theme(strip.text.x = element_blank(),
       strip.text.y = element_text(size = 10),
        axis.title = element_blank(),
        # strip.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 10),
        # axis.text.y = element_blank(),
        # axis.text.y = element_text(size = 5),
         axis.text.x = element_blank(),
        axis.ticks.x.bottom = element_blank(),
        axis.ticks.y.left = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank())

@@

NichesOMZNorth <- PhotoperiodDepthOMZ %>%
  filter(lat == 45) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 5) %>% 
mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
         lat = factor(lat, levels = c("45", "0"))) %>%
ggplot()+
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
            size = 0.5, alpha = 0, show.legend = TRUE)+
   labs(title = "OMZ") +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
    facet_grid(rows = vars(lat),
              cols = vars(DayofYear),
              labeller = labeller(lat = label_both)) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
   # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 3
  )  +
  guides(color = "none") +
  theme_bw() +
 theme(strip.text.x = element_text(size = 10),
       strip.text.y = element_text(size = 10),
        axis.title = element_blank(),
        # strip.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 10),
        # axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x.bottom = element_blank(),
        axis.ticks.y.left = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank())

@@

NichesOMZEquat <- PhotoperiodDepthOMZ %>%
  filter(lat == 0) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 5) %>% 
mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
         lat = factor(lat, levels = c("45", "0"))) %>%
ggplot()+
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
            size = 0.5, alpha = 0, show.legend = TRUE)+
  # labs(title = "Full Oxygen") +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
    facet_grid(rows = vars(lat),
              cols = vars(DayofYear),
              labeller = labeller(lat = label_both)) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
   # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 3
  )  +
  guides(color = "none") +
  theme_bw() +
 theme(strip.text.x = element_blank(),
       strip.text.y = element_text(size = 10),
        axis.title = element_blank(),
        # strip.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 10),
        # axis.text.y = element_blank(),
         axis.text.x = element_blank(),
        axis.ticks.x.bottom = element_blank(),
        axis.ticks.y.left = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank())

@@
